Asymmetric continuous prediction bands for assessing the validity of smooth biomechanical curve data

### 2021-09-16 paper.Rmd
Modify plots

PLOT <- ggplot(data = data.single.mc, aes(x = frame, y = value, group = strideID)) + # , colour = subjectID
  geom_line(alpha = 0.7) +
  geom_line(data = data.single.imu, aes(x = frame, y = value, group = strideID, col = "red"), alpha = 0.3) + #, colour = subjectID
  labs(x = "Time-normalized signal [%]", y = "Difference") +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 20),
        axis.title.x = element_text(size = 22),
        axis.text.y = element_text(size = 20),
        axis.title.y = element_text(size = 22),
        legend.position = "none")

>>>>

PLOT <- ggplot(data = data.single.mc, aes(x = frame, y = value, group = strideID)) +
  geom_line() +
  scale_color_grey(start = 0.6, end = 0.9) +
  geom_line(data = data.single.imu, aes(x = frame, y = value, group = strideID, colour = as.factor(subjectID)), alpha = 0.3) +
  labs(x = "Time-normalized signal [%]", y = "Signal value") +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 20),
        axis.title.x = element_text(size = 18),
        axis.text.y = element_text(size = 20),
        axis.title.y = element_text(size = 18),
        legend.position = "none")
